Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Updated Figure 11

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.45, -0.2)) +
  ylim(c(-0.15, 0.18)) +
  interior_annotation("a", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0.05, 0.25)) +
  ylim(c(-0.15, 0.25)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.25, 0.1)) +
  ylim(c(-0.9, -0.55)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0, 0.4)) +
  ylim(c(-0.15, 0.3)) +
  interior_annotation("d", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

# axes_obj <- gen_axes(
#   data = scaled_gau_data, 
#   proj_data = projected_df, 
#   limits = 1)
# 
# axes <- axes_obj$axes
# circle <- axes_obj$circle

limits <- 0.3
projected_df_n <- projected_df |> select(-ID)

rng <- range(projected_df_n)
projected_df_n <- projected_df_n/max(abs(rng))
colnames(projected_df_n) <- c("P1", "P2")
projected_df_n <- data.frame(projected_df_n)
obs_labels <- as.character(1:nrow(scaled_gau_data))

axis_scale <- limits/6
# axis_pos <- -2/3 * limits
axis_pos <- 0

axis_labels <- colnames(scaled_gau_data)
rownames(axes) <- axis_labels

theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), 
                     c2 = adj(sin(theta)))

five_gau_proj_pacmap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.05, 0.35)) +
  ylim(c(-0.05, 0.35)) +
  interior_annotation("e", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

# axes_obj <- gen_axes(
#   data = scaled_gau_data, 
#   proj_data = projected_df, 
#   limits = 1)
# 
# axes <- axes_obj$axes
# circle <- axes_obj$circle

limits <- 0.3
projected_df_n <- projected_df |> select(-ID)

rng <- range(projected_df_n)
projected_df_n <- projected_df_n/max(abs(rng))
colnames(projected_df_n) <- c("P1", "P2")
projected_df_n <- data.frame(projected_df_n)
obs_labels <- as.character(1:nrow(scaled_gau_data))

axis_scale <- limits/6
# axis_pos <- -2/3 * limits
axis_pos_x <- -0.05
axis_pos_y <- -0.4

axis_labels <- colnames(scaled_gau_data)
rownames(axes) <- axis_labels

>>>>

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.45, -0.2)) +
  ylim(c(-0.15, 0.18)) +
  interior_annotation("a", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0.05, 0.25)) +
  ylim(c(-0.15, 0.25)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.25, 0.1)) +
  ylim(c(-0.9, -0.55)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0, 0.4)) +
  ylim(c(-0.15, 0.3)) +
  interior_annotation("d", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.3,
  axis_pos_x = 0.1,
  axis_pos_y = 0.05)

five_gau_proj_pacmap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0.05, 0.35)) +
  ylim(c(0, 0.35)) +
  interior_annotation("e", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.3,
  axis_pos_x = -0.05,
  axis_pos_y = -0.4)
